PHAT RAID, yo

### 2014-05-14 paper/paper.tex
Update paper

>>>>

\begin{figure}
  \includegraphics[scale=0.45]{Store.pdf}
  \caption{Scatter Plot of Various \phatraidcf{$C$,$f$} Configurations}
  \label{fig:plot}
\end{figure}

We evaluated a prototype \phatraidcf{C}{f} implementation. We simulated disk
latency with sleeps. All experiments are run on a 2013-model MacBook Pro with
8GB of RAM, and a 3GHz Intel Core i7. We found that latency scales as
$\frac{1}{C-1}$. This is the expected behavior for breaking a file into $C-1$
chunks. We always use one bit of parity.

As expected \phatraidcf{2}{$f$} does not perform better than non-RAID \phat{}
(i.e. \phatraidcf{1}{$f$}) because the data is not sharded into pieces, and the
parity bit acts as a complete duplicate of the file.
